Trends in asymmetric drift across the blue cloud

### 2018-04-04 ms.tex
minor updates

\slugcomment{Draft: 14 Feb 2017}

@@

\newcommand{\kms}{{km$~\!$s$^{-1}$}}
\newcommand{\nsaz}{$z_{\rm NSA}$}
\newcommand{\halpha}{H$\alpha$}

@@

\title{ The trend in asymmetric drift across the blue cloud }

@@

\altaffiltext{1}{UCO/Lick Observatory, University of California, Santa
Cruz, 1156 High St., Santa Cruz, CA 95064, USA}

\altaffiltext{2}{Department of Astronomy, University of Wisconsin-Madison, 475
N. Charter St., Madison, WI 53706, USA}

@@

Asymmetric drift (AD) is the lag of the mean rotation velocity of the
stellar disk behind the circular speed defined by the total
gravitational potential.  Although it is often considered a nuisance
correction one must apply in circular-speed calculations, the direct
connection between AD and the stellar phase-space distribution function
makes it an interesting dynamical properties of galaxies in and of
itself.  The SDSS-IV/MaNGA survey provides more than an order of
magnitude increase in any galaxy sample size useful for AD measurements.
In this pilot study, we demonstrate the empirical correlation between
AD, or more precisely the differential tangential lag between the
stellar component and \halpha-emitting gas, and global photometric
properties from the NASA-Sloan Atlas.  We isolate a set of galaxies with
\halpha\ and stellar velocity fields that are well-fit by simple disk
models.  Our sample of $\sim$800 galaxies shows a clear correlation
between absolute $i$-band magnitude and AD measured at half an effective
radius.  Removing the primary dependence on the rotation speed, we find
that the stellar disk rotation is 90\% of the \halpha\ rotation speed,
in the mean.  Our sample size allows us to infer a weak, yet
statistically significant, trend with galaxy $N-r$ color such that, in
the mean, redder galaxies have moderately larger AD relative to their
rotation speeds.  Within the context of an albeit strong set of
assumptions, including a direct proportionality between AD and stellar
velocity dispersion as seen in the Milky Way, we argue that our results
suggest little variation in the mean disk mass-to-light ratio as a
function of absolute magnitude and only modest variations with galaxy
color \comment{last sentence TBD; is Figure 3 consistent with SPS
variations?}.

@@

For ensembles of stars in a galaxy disk, \citet[][Section
4.4.3]{2008gady.book.....B} provide an intuitive description of
asymmetric drift (AD) as arising due to the combined effect of the
radially decreasing surface-density and velocity-dispersion profiles
typical of axisymmetric systems.  Using the $v_R$ moment of the
collisionless Boltzmann equation, one obtains the Jeans equation
\citep{Jeans1919} that directly relates the circular speed ($v_c$), the
mean stellar tangential speed ($\overline{v_\theta}$), and the stellar
velocity ellipsoid (SVE) as a function of radius in the plane of
symmetry:
%
\begin{equation}
%
v_c^2 - \overline{v_\theta}^2 = \sigma_R^2\left[
\frac{\sigma_\theta^2}{\sigma_R^2} -
\frac{R}{\rho\sigma_R^2}\frac{\partial(\rho\sigma_R^2)}{\partial R} -
1\right] - R\frac{\partial\overline{v_R v_z}}{\partial z},
%
\label{eq:adformal}
%
\end{equation}
%
where $R,\theta,z$ are the cylindrical coordinates, $\rho$ is the volume
density, and $\sigma$ is the velocity dispersion.  Along with the
standard assumptions of dynamical equilibrium and negligible radial and
vertical flows inherent to its derivation, equation \ref{eq:adformal} is
often simplified by assuming the right-most term --- describing the
covariance between the radial and vertical motions as a function of
perpendicular distance to the plane of symmetry --- is negligible
\citep{1991ApJ...368...79A}.

Asymmetric drift has been measured in numerous systems.  Perhaps most
notably, e.g., \comment{Dehnen \& Binney} have shown that populations of
stars show a direct correlation between their velocity dispersion and
the degree to which their mean rotation speed lags behind that of the
Local Standard of Rest (LSR), much in line with the expectation provided
by equation \ref{eq:adformal}.  Although there have been some studies of
AD in external galaxies \comment{refs}, it is often treated as a
nuisance phenomenon that must be corrected for when trying to constrain
the circular speed of a galaxy \comment{refs}.  The ubiquity and
phenomenology of AD as a salient observable has not yet been studied for
a statistically significant population of galaxies.  Our aim is
therefore to provide a first look at the correlation between AD
measurements and basic broad-band photometric properties for a large
sample of galaxies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
%
\begin{center}
%
\includegraphics[width=0.9\textwidth]{figs/cmd_flux.pdf}
%
\end{center}
%
\caption{
%
${\rm N} - r$ color and absolute $i$-band magnitude ($M_i$) for all
galaxies observed during the first two years of the MaNGA Survey (left),
the subsample of galaxies {\em not} selected to be kinematically regular
(middle; see text), and the AD sample used throughout the remainder of
our analysis.  The color of the data points in the top row represent the
mean \halpha\ surface brightness \comment{check aperture} according to
the colorbar to the right; the bottom row replaces the color by the
$r$-band surface brightness density.
%
}
%
\label{fig:sample}
%
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In addition to the basic understanding of this dynamically relevant
quantity, our interest in AD stems from its fundamental dynamical
connection to the full phase-space distribution function of a galaxy's
stars, as empirically demonstrated in the Milky Way.  Indeed,
\citet{2011ApJ...742...18W} used AD to constrain the axial ratios of the
SVE given direct measurements of the line-of-sight (LOS) stellar
velocity dispersion, $\sigma$.  Alternatively, if one can leverage
statistical constraints on the shape of the SVE
\citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD can be used as a
proxy for stellar $\sigma$ via equation \ref{eq:adformal}.  Such a use
of AD-$\sigma$ relation is attractive in the low-surface-brightness and
low-velocity-dispersion regimes where direct measurements are difficult
and/or expensive.  We commit to this paradigm by using the following
nomenclature for AD, following from equation \ref{eq:adformal}:
%
\begin{equation}
%
\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2.
%
\label{eq:addef}
%
\end{equation}

For disk galaxies, there is a decades-long industry of using cold-gas
tracers to construct circular-speed curves of galaxies \comment{refs}.
These data have provided the first concrete arguments for the presence
of massive dark-matter halos \comment{ref} based on mass-model
reconstruction \comment{refs} and have formed the basis for the most
robust Tully-Fisher relations compiled for the local Universe
\comment{refs}.  However, it is important to acknowledge that one cannot
directly measure $v_c$, effectively making $\sigma_a$ unobservable.
That is, every dynamical tracer has some non-zero dynamical pressure
such that it will lag behind the theoretically defined circular speed.
There are very clear examples of early-type galaxies that show
differential AD in their molecular (e.g., CO), atomic (e.g.,
\ion{H}{1}), and/or ionized (\halpha) tracers relative to a robust mass
model of $v_c$ \comment{Davis et al.}, due to the different
turbulent/thermal pressures intrinsic to these tracers.  However, these
signatures are much less apparent in disk galaxies.  For example,
\comment{Martinsson et al.} show that \halpha\ and \ion{H}{1} rotation
curves are consistent for the DiskMass Survey within the limits of their
constraints on beam-smearing, suggesting that any correction for the lag
of either behind the circular speed should be small.  Indeed,
theoretical calculations \comment{Dalcanton \& Stilp} suggest that
gas-pressure corrections to \ion{H}{1} rotation curves should be largely
negligible for galaxies with \comment{${\mathcal M} > 10^x {\mathcal
M}_\odot$}.  Nevertheless, we emphasize here that our measurements of
$\sigma_a$ may be better termed as a {\em differential tangential lag}
because they are based on the quadrature difference between the observed
\halpha\ and stellar rotation curves in our galaxy sample (Section
\ref{sec:data}).  These measurements are perfectly valid in their own
right; however, it is their interpretation in the context of the
theoretical definition of AD that should be questioned in some regimes,
as discussed in Section \ref{sec:discussion}.

@@

We use integral-field spectroscopy from the SDSS-IV/MaNGA (Mapping
Nearby Galaxies from APO) Survey to construct stellar and ionized-gas
velocity fields for 2715 unique galaxies, 39 of which have multiple
observations.  The kinematic measurements are provided by the MaNGA data
analysis pipeline \comment{DAP; Westfall et al., in prep}: the
ionized-gas kinematics are based on simple single-Gaussian fits to the
\halpha\ emission feature and the stellar kinematics are determined
using {\tt pPXF} (Cappellari et al.) with the MILES stellar template
library \comment{Jesus FB et al.}.  \comment{Mention hierarchical
clustering?}

The MaNGA galaxy selection \citep{2017AJ....154...86W} is a simple cut
in absolute $i$-band magnitude, $M_i$, and redshift, $z$, and provides a
complete sampling of the overall galaxy population.  As such,
measurements of stellar and/or \halpha\ rotation curves for some systems
will be difficult/impossible.  Using the photometry from the NASA-Sloan
Atlas,\footnote{\url{nsatlas.org}} Figure \ref{fig:sample} shows the
color-magnitude diagram of all galaxies colored by their mean \halpha\
and $r$-band surface brightness.  \comment{Update this} Although not
excluded from our velocity-field analysis {\em a priori}, we expect to
obtain poor rotation-curve measurements for galaxies with low \halpha\
and stellar surface brightness.\footnote{
%
The uniformity of the MaNGA survey \citet{2015AJ....150...19L} is such
that the signal-to-noise (S/N) of the datacube spaxels is tightly
correlated with surface brightness.}

@@

We model the geometric projection of the rotational plane of each galaxy
using the approach presented by \citep[][see also
\citealt{2011ApJ...742...18W}]{2003ApJ...599L..79A}.  In three
independent fitting iterations, the model fits are optimized for the
\halpha\ velocity field, the stellar velocity field, and simultaneously
for both data sets; for the latter, the geometry is forced to be the
same for the two dynamical tracers, but the parametrized rotation curves
are independent.  We use these velocity-field-fitting results to
objectively isolate a set of ``kinematically regular'' galaxies.
Briefly, galaxies in this sample must have: (i) successful
velocity-field fits for all three approaches, (ii) differences in the
measured \halpha\ and stellar systemic velocity of less than 20 km/s,
(iii) dynamical centers that are consistent to within a fiber diameter
of the morphological center \comment{check the details of this}, (iv)
\halpha\ and stellar velocity-field position angles that are consistent
to within $\pm$15$\arcdeg$, and (v) kinematic inclinations between
$15\arcdeg < i < 80\arcdeg$ that are both consistent between the
\halpha\ and stellar data and with respect to the photometric
ellipticity to within $\pm$20$\arcdeg$.  The constraint on the
inclination is by far the most stringent. \comment{give number of
galaxies cut by each criterion?}  Applying these constraints yields a
sample of 798 observations (for 790 unique galaxies) out of the 2764
observations analyzed.  Eleven galaxies with repeat observations satisfy
the selection criteria; however, only five of these show all
observations are consistently selected.  The remaining six show one or
more of the observations did not pass our constraints \comment{we should
understand why repeat observations are not consistent for the majority
of cases.  low S/N?}.  \comment{Do this or remove the sentence:}
Finally, we also visually inspected the broad-band imaging of these 790
galaxies and eliminated merging and highly extincted (highly inclined)
systems yielding a final sample of XXX galaxies.  We hereafter refer to
galaxies that satisfy our selection criteria as the ``AD sample''.

>>>>

\slugcomment{Draft: 22 Jan 2018}

@@

% Some shorthands
\newcommand{\kms}{{km$~\!$s$^{-1}$}}
\newcommand{\nsaz}{$z_{\rm NSA}$}
\newcommand{\halpha}{H$\alpha$}

@@

\title{ Trends in asymmetric drift across the blue cloud }

@@

\altaffiltext{1}{University of California Observatories, University of
California Santa Cruz, 1156 High St., Santa Cruz, CA 95064, USA}

\altaffiltext{2}{Department of Astronomy, University of Wisconsin--Madison, 475
N. Charter St., Madison, WI 53706, USA}

@@

Asymmetric drift (AD) is the lag of the mean rotation velocity of the
stellar disk behind the circular speed defined by the total
gravitational potential.  Although it is often considered a nuisance
correction one must apply in circular-speed calculations, the direct
connection between AD and the stellar phase-space distribution function
makes it an interesting dynamical properties of galaxies in and of
itself.  The SDSS-IV/MaNGA survey provides more than an order of
magnitude increase in any galaxy sample size useful for AD measurements.
In this pilot study, we measure AD --- or more precisely the
differential tangential lag between the stellar component and
\halpha-emitting gas --- in a set of galaxies with \halpha\ and stellar
velocity fields that are well-fit by simple disk models.  We describe
our fitting approach and the selection of our subsample in detail.  Our
final sample of $\sim$XXX galaxies shows a clear correlation between
absolute $i$-band magnitude and AD measured at effectively all radii.
\comment{The rest neesds to be updated.} Removing the primary dependence
on the rotation speed, we find that the stellar disk rotation is 90\% of
the \halpha\ rotation speed, in the mean.  Our sample size allows us to
infer a weak, yet statistically significant, trend with galaxy $N-r$
color such that, in the mean, redder galaxies have moderately larger AD
relative to their rotation speeds.  Within the context of an albeit
strong set of assumptions, including a direct proportionality between AD
and stellar velocity dispersion as seen in the Milky Way, we argue that
our results suggest little variation in the mean disk mass-to-light
ratio as a function of absolute magnitude and only modest variations
with galaxy color \comment{last sentence TBD; is Figure 3 consistent
with SPS variations?}.

@@

For ensembles of stars in a galaxy disk, \citet[][Section
4.4.3]{2008gady.book.....B} provide an intuitive description of
asymmetric drift (AD).  The combined effect of the radially decreasing
surface-density and velocity-dispersion profiles, typical of
axisymmetric systems like the Milky Way, leads to an asymmetric velocity
distribution function with a mean value less than the circular speed
defined by the gravitational potential.  The standard mathematical
representation of this is derived by taking the $v_R$ moment of the
collisionless Boltzmann equation to find the Jeans equation
\citep{Jeans1919} that directly relates the circular speed ($v_c$), the
mean stellar tangential speed ($\overline{v_\theta}$), and the stellar
velocity ellipsoid (SVE) as a function of radius in the plane of
symmetry:
%
\begin{equation}
%
v_c^2 - \overline{v_\theta}^2 = \sigma_R^2\left[
\frac{\sigma_\theta^2}{\sigma_R^2} -
\frac{R}{\rho\sigma_R^2}\frac{\partial(\rho\sigma_R^2)}{\partial R} -
1\right] - R\frac{\partial\overline{v_R v_z}}{\partial z},
%
\label{eq:adformal}
%
\end{equation}
%
where $R,\theta,z$ are the cylindrical coordinates, $\rho$ is the volume
density, and $\sigma$ is the velocity dispersion.  Along with the
standard assumptions of dynamical equilibrium and negligible radial and
vertical flows inherent to its derivation, equation \ref{eq:adformal} is
often simplified by assuming the right-most term --- describing the
covariance between the radial and vertical motions as a function of
perpendicular distance to the plane of symmetry --- is negligible
\citep[cf.][]{1991ApJ...368...79A}.

Asymmetric drift has been measured in numerous systems, perhaps most
notably in the Galaxy.  For example, \citet{1998MNRAS.298..387D} have
shown that populations of stars show a direct correlation between their
velocity dispersion and the degree to which their mean rotation speed
lags behind that of the Local Standard of Rest (LSR), much in line with
the expectation provided by equation \ref{eq:adformal} (see also
\comment{more recent RAVE and RAVE+Gaia references}).

Asymmetric drift measurements in extragalactic systems are common in the
literature \ref{examples}; however, it is most often cast as a nuisance
phenomenon that one must correct for when constructing circular-speed
curves \comment{refs}.  The ubiquity and phenomenology of AD as a
salient observable has not yet been studied for a statistically
significant population of galaxies.  Our aim is therefore to provide a
first look at the correlation between AD measurements and basic
broad-band photometric properties for a large sample of galaxies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
%
\begin{center}
%
\includegraphics[width=0.9\textwidth]{figs/cmd_flux.pdf}
%
\end{center}
%
\caption{
%
${\rm NUV} - r$ color and absolute $i$-band magnitude ($M_i$) from the
NASA-Sloan Atlas (NSA) for all galaxies observed during the first two
years of the MaNGA Survey (left), the subsample of galaxies {\em not}
selected to be kinematically regular (middle; see text), and the AD
sample used throughout the remainder of our analysis.  The color of the
data points in the top row represent the mean \halpha\ surface
brightness within the elliptical-Petrosian half-light radius according
to the colorbar to the right; the bottom row replaces the color by the
mean $g$-band surface brightness density over the same elliptical
aperture.
%
}
%
\label{fig:sample}
%
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In addition to a basic characterization of the phenomenon, our interest
in AD stems from its fundamental dynamical connection to the full
phase-space distribution function of a galaxy's stars, as empirically
demonstrated in the Milky Way.  Indeed, \citet{2011ApJ...742...18W} used
AD to constrain the axial ratios of the SVE given direct measurements of
the line-of-sight (LOS) stellar velocity dispersion, $\sigma$.
Alternatively, if one can leverage statistical constraints on the shape
of the SVE \citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD can
be used as a proxy for stellar $\sigma$ via equation \ref{eq:adformal}.
Such a use of AD-$\sigma$ relation is attractive in the
low-surface-brightness and low-velocity-dispersion regimes where direct
measurements are difficult and/or expensive.  We commit to this paradigm
by defining $\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2$, following
from equation \ref{eq:adformal}, for use throughout this paper.

For disk galaxies, there is a decades-long industry of using cold-gas
tracers to construct circular-speed curves of galaxies \comment{refs}.
These data have provided the first concrete arguments for the presence
of massive dark-matter halos \comment{ref} based on mass-model
reconstruction \comment{refs} and have formed the basis for the most
robust Tully-Fisher relations compiled for the local Universe
\comment{refs}.  However, it is important to acknowledge that one cannot
directly measure $v_c$, effectively making $\sigma_a$ unobservable.
That is, every dynamical tracer has some non-zero dynamical pressure
such that it will lag behind the theoretically defined circular speed.
There are very clear examples of early-type galaxies that show
differential AD in their molecular (e.g., CO), atomic (e.g.,
\ion{H}{1}), and/or ionized (\halpha) tracers relative to a robust mass
model of $v_c$ \citep{2013MNRAS.429..534D}, due to the different
turbulent/thermal pressures intrinsic to these tracers.  However, these
signatures are much less apparent in disk galaxies.  For example,
\citet{2013A&A...557A.131M} show that \halpha\ and \ion{H}{1} rotation
curves are consistent for the DiskMass Survey within the limits of their
constraints on beam-smearing.  This suggests that any correction for the
lag behind the circular speed of either the \halpha- or
\ion{H}{1}-emitting gas should be small.  Indeed, theoretical
calculations \citet{2010ApJ...721..547D} suggest that gas-pressure
corrections to \ion{H}{1} rotation curves should be largely negligible
for galaxies with circular speeds larger than roughly 75 \kms.
Nevertheless, we emphasize here that our measurements of $\sigma_a$ may
be better termed as a {\em differential tangential lag} because they are
calculated as the quadrature difference between the {\em observed}
\halpha\ and stellar rotation curves in our galaxy sample (Section
\ref{sec:data}).  These measurements are perfectly valid in their own
right; however, their interpretation in the context of the theoretical
definition of AD must be done with care, as we discuss in Section
\ref{sec:discussion}.

@@

We use integral-field spectroscopy from the SDSS-IV/MaNGA (Mapping
Nearby Galaxies from APO) Survey to construct stellar and ionized-gas
velocity fields for 2715 unique galaxies, 39 of which have multiple
observations.  These data were obtained during the first two years of
normal survey operations, and the reduced datacubes are included in DR14
\citep{2017arXiv170709322A}.  \comment{additional references to
technical papers}.

The kinematic measurements are determined by a preliminary version of
the MaNGA data analysis pipeline (DAP; Westfall et al., in prep).  From
this preliminary version (2.0.2), we use the simple single-Gaussian fits
to the \halpha\ emission feature for the ionized-gas kinematics, and the
stellar kinematics are determined using {\tt pPXF}
\citep{2004PASP..116..138C, 2017MNRAS.466..798C} with the MILES stellar
template library \citep{2011A&A...532A..95F}.  We find the velocity
measurements to be statistically well behaved to a $g$-band
signal-to-noise ratio (SNR) of $\sim$1.\footnote{
%
This and other assessments of the fidelity of the stellar kinematics
provided by the DAP will be discussed in detail by Westfall et al., {\em
in prep}.}
%
Therefore, we perform our analysis using the stellar kinematics measured
for each MaNGA spaxel (each spaxel is $0\farcs5$ on a side and
subsamples the $\sim$$2\farcs5$ fiber beam).

% \comment{Mention hierarchical clustering?}

The MaNGA galaxy selection, see \citet{2017AJ....154...86W}, is a simple
cut in absolute $i$-band magnitude, $M_i$, from the NASA-Sloan Atlas
(NSA; \url{www.nsatlas.org}) and the SDSS single-fiber redshift, $z$.
The MaNGA galaxy sample provides a statistically complete representation
of the overall galaxy population with a provided set of corrections to a
volume-limited sample.  The NSA-based ($N-r, M_i$) color-magnitude
diagram (CMD) of the full sample of galaxies obtained through the second
year of survey operations are shown in the left-most panels of Figure
\ref{fig:sample}, with the points colored by the \halpha\ .

Using the photometry from the NSA, Figure \ref{fig:sample} shows the
color-magnitude diagram of all galaxies colored by their mean \halpha\
and $r$-band surface brightness.

However, our nominal approach to measuring the stellar and gas rotation curves will be limited forAs such,
measurements of stellar and/or \halpha\ rotation curves for some systems
will be difficult/impossible.

\comment{Update this} Although not
excluded from our velocity-field analysis {\em a priori}, we expect to
obtain poor rotation-curve measurements for galaxies with low \halpha\
and stellar surface brightness.\footnote{
%
The uniformity of the MaNGA survey \citet{2015AJ....150...19L} is such
that the signal-to-noise (S/N) of the datacube spaxels is tightly
correlated with surface brightness.}

@@

We model the geometric projection of the rotational plane of each galaxy
using the approach presented by \citep[][see also
\citealt{2011ApJ...742...18W}]{2003ApJ...599L..79A}.  In three
independent fitting iterations, the model fits are optimized for the
\halpha\ velocity field, the stellar velocity field, and simultaneously
for both data sets; for the latter, the geometry is forced to be the
same for the two dynamical tracers, but the parametrized rotation curves
are independent.  We use these velocity-field-fitting results to
objectively isolate a set of ``kinematically regular'' galaxies.
Briefly, galaxies in this sample must have: (i) successful
velocity-field fits for all three approaches, (ii) differences in the
measured \halpha\ and stellar systemic velocity of less than 20 \kms,
(iii) dynamical centers that are consistent to within a fiber diameter
of the morphological center \comment{check the details of this}, (iv)
\halpha\ and stellar velocity-field position angles that are consistent
to within $\pm$15$\arcdeg$, and (v) kinematic inclinations between
$15\arcdeg < i < 80\arcdeg$ that are both consistent between the
\halpha\ and stellar data and with respect to the photometric
ellipticity to within $\pm$20$\arcdeg$.  The constraint on the
inclination is by far the most stringent. \comment{give number of
galaxies cut by each criterion?}  Applying these constraints yields a
sample of 798 observations (for 790 unique galaxies) out of the 2764
observations analyzed.  Eleven galaxies with repeat observations satisfy
the selection criteria; however, only five of these show all
observations are consistently selected.  The remaining six show one or
more of the observations did not pass our constraints \comment{we should
understand why repeat observations are not consistent for the majority
of cases.  low S/N?}.  \comment{Do this or remove the sentence:}
Finally, we also visually inspected the broad-band imaging of these 790
galaxies and eliminated merging and highly extincted (highly inclined)
systems yielding a final sample of XXX galaxies.  We hereafter refer to
galaxies that satisfy our selection criteria as the ``AD sample''.
